A new framework for recovering the mass and redshift dependence\\ of galaxy pair fractions across cosmic time

### 2023-09-22 paper/pears.tex
submitting to arxiv!

% Packages
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{soul}

@@

% Affiliations
\newcommand{\affuofa}{University of Arizona, 933 N. Cherry Ave,
    Tucson, AZ 85721, USA}

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

@@

\title{
  % Pair fractions of low mass and high mass galaxy pairs in the TNG100 cosmological simulation
  % low mass and high mass galaxy pairs evolve differently as a function of redshift
  A new framework for recovering the mass and redshift dependence\\ of galaxy pair fractions across cosmic time }
% Differences in the redshift evolution of low mass and high mass galaxy pairs in the TNG100 cosmological simulation

\author[0000-0001-8765-8670]{Katie~Chamberlain}
\affiliation{\affuofa}

@@

\author{others}

\begin{abstract}
Low mass galaxy pair fractions are understudied across cosmic time. 
In the era of JWST, a self-consistent framework is needed to select both low and high mass galaxy pairs in order to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts. 
Here, we construct a sample of low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) subhalo pairs from the TNG100 simulation from $z=0-4.2$. 
Pairs belong to the same FoF group, meaning they are isolated, physically associated, and not contaminated by projection effects. 
Stellar masses are assigned using abundance matching. 
We find that the low mass pair fraction increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. 
At z=0 the low mass major pair fraction is four times lower than that of high mass pairs, consistent with findings for cosmological merger rates. 
Our results indicate that pair fractions can faithfully reproduce trends in merger rates if galaxy pairs are selected appropriately. 
Specifically, static pair separation limits applied equivalently to all galaxy pairs do not recover the evolution of low and high mass pair fractions. 
Instead, we advocate for separation limits that vary with the mass and redshift of the system, such as separation limits scaled by the estimated virial radius of the pair ($r_{sep}< 1 R_{vir}$). 
Finally, we place isolated mass-analogs of Local Group galaxy pairs (MW--M31, MW--LMC, M31--M33, LMC--SMC) in a cosmological context, quantifying for the first time the frequency of finding isolated analogs of such pairs as a function of redshift.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{sec:intro}
    Galaxy mergers have been studied in detail as a mechanism for driving galaxy evolution, and have been identified as a trigger of, for example, 
    active galactic nuclei (AGN)~\citep[e.g.][]{Hopkins2008,Comerford2015,Blecha2018,Ellison2019}, 
    star formation~\citep[e.g.][]{Mihos1996, DiMatteo2008,Patton2013, Hopkins2013,Patton2020,Hani2020}, 
    and changes in morphology~\citep[e.g.][]{Conselice2003,Lotz2008,Casteels2014,RG2017,Guzman-Ortega2023}. 
    Constraining the merger rate for galaxies is critical for quantifying the importance of mergers for galaxy evolution and testing predictions for hierarchical assembly in cold dark matter theory \citep[e.g.][]{Stewart2009,Hopkins2010,RG2015}.

    In practice, merger rates cannot be measured straightforwardly from observations and, rather, are calculated by converting the observed frequency of a galaxy merger signature (i.e., asymmetry, concentration, pair fraction, etc.) to a merger rate using an observability timescale~\citep[e.g.][]{Lotz2011}. 
    Low mass galaxies are most often morphologically disturbed by fly-bys and non-merger interactions~\citep{Martin2021}, and star forming galaxies at high redshift tend to be clumpy and asymmetric, even in isolation~\citep{Wuyts2013}, thus pair fractions offer the most robust method of observationally quantifying merger rates across cosmic time.

    Pair fractions of high mass ($M_*\gtrsim10^{10}\Msun$) galaxies have been well studied across cosmic time both observationally~\citep[e.g.][]{Patton2000,Lotz2011,Ferreras2014, Man2016,Duncan2019}, and theoretically~\citep[e.g.][]{RG2015,Snyder2017,Snyder2023}, with theoretical studies typically done in projection for comparison to observational campaigns. 
    Low mass galaxy pairs ($10^8<M_*<5\times10^9\Msun$) have been studied at low redshift~\citep[e.g.][]{Stierwalt2015,Pearson2016,Besla2018,Paudel2018,Luber2022},
    but are less well understood across cosmic time owing to the difficulty in observing faint systems outside of the Local Volume. 
    However, JWST will significantly revolutionize our ability to find such systems at higher redshift~\citep{Behroozi2020}.

    There are reasons to believe that low mass and high mass pairs evolve differently as a function of time.
    For example, semi-empirical and cosmological studies find that galaxy merger rates vary both with redshift and the mass of the most massive galaxy of the pair~\citep[see e.g.][]{Stewart2009,Hopkins2010,RG2015}.
    % Such differences are likely to give rise to differences in the pair fractions of low and high mass pairs.
    It is thus reasonable to assume that the pair fractions of these two mass scales reflect these evolutionary differences as well.

@@

    In this study, we take the approach of self-consistently selecting physically associated pairs of low mass ($10^8<M_*<5\times10^9\Msun$) and high mass $(5\times10^9<M_*<10^{11}\,\Msun)$ galaxies. 
    Specifically, we identify major ($1-1/4$) and minor $(1/10-1/4)$ pairs from $z=0-4.2$ in the IllustrisTNG cosmological simulation, TNG100. 
    We require that pairs are part of the same FoF group and that no other more massive perturbers are nearby, which allows us to ensure that the recovered pair fractions are inherent to the population of selected pairs rather than a function of environment.

    Typically, observational studies of pair fractions apply projected separation cuts that are constant over time and do not vary with the mass of the target system. 
    To fairly test for differences in the evolutionary behavior of pair fractions, especially in observational studies, it is necessary to determine whether this is an appropriate technique for faithfully recovering true pair fraction behavior.
    In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and make recommendations for a time and mass evolving separation cut to permit equitable pair fraction comparisons between different mass regimes.

@@

    This paper is structured as follows. 
    In Section~\ref{sec:methods}, we outline our methodology for selecting physically associated high mass and low mass pairs from the TNG simulation. 
    In Section~\ref{sec:pairprops}, we provide an overview of properties of the selected sample, including the number of primaries, pairs, and their stellar mass ratios as a function of time. 
    We present the time evolving pair fraction of high mass and low mass pairs in Section~\ref{sec:results}, and show how they change for different separation criteria. 
    In Section~\ref{sec:discussion}, we discuss the implications of the differences between low and high mass pair fractions for observational campaigns and give context to our results by drawing comparisons to Local Group pairs. 
    Finally, we summarize our results and conclusions in Section~\ref{sec:summary}.

@@

\section{Methodology}\label{sec:methods}
We aim to quantify and characterize the frequency, or pair fraction, of low mass ($\rm\ms{}=10^{8}-5\times 10^{9}\Msun$) and high mass ($\rm\ms{}=5\times10^{9}-10^{11}\Msun$) galaxy pairs in cosmological simulations as a function of cosmic time. 
To this end, we utilize the \tng\ simulation to select subhalo pairs as a function of redshift, according to the selection criteria outlined in the remainder of this section.

@@

%%%%%%%%%%%%%%%%%%%%%%%
% Sim details section %
    \subsection{Simulation details} \label{sec:methods-sims}
        % Brief description of TNG hydro and which run we use.
    The IllustrisTNG project~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body and full physics cosmological simulations that adopt the \textit{Planck2015} \lcdm\  cosmology~\citep{Planck2015}.
    % GB edited below 
    In this study we utilize data from TNG100-1, the main high resolution, full physics simulation of a (110.7\Mpc)$^3$ volume (hereafter TNG100). 
    This simulation follows the evolution of baryons and $1820^3$ dark matter particles from $z=127$ to $z=0$.  
    The volume of this simulation is sufficiently large, and resolution is sufficiently high, to conduct a simultaneous analysis of the statistics of both low mass and high mass galaxy pairs, as shown by studies of pair statistics in similarly sized volumes~\citep{Sales2013,Patel2017a-Orbits,Patel2017b-Masses,Besla2018}. % more?

      % subfind, sublink, and groups and subhalos
    We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm~\citep{Springel2001,Dolag2009}. 
    This catalog was created using the Friends-of-Friends (FoF) algorithm~\citep{Davis1985}, which links nearby particles to define large halos of associated particles, from which subhalos are identified as over-dense and gravitationally bound dark matter structures.
    In addition, we utilize the merger trees provided by the \texttt{SUBLINK} algorithm~\citep{RG2015}, which tracks subhalos between snapshots, enabling us to trace the mass evolution of our selected subhalos.

    % Baryonic process are known to affect the structure and formation of dark matter halos of low mass ($M_*\lesssim 1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
    % Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback and reionization~\citep{}, resulting in fewer low mass halos ($\lesssim 5\times10^{10}$) in hydrodynamic simulations~\citep{vogelsberger14B}.
% End sim details     %
%%%%%%%%%%%%%%%%%%%%%%%

@@

    In this section, we outline the steps to create the \subcat, which we will utilize to assign stellar masses to each of the dark matter subhalos to create our low mass and high mass galaxy catalogs.

    % GB edited 
    We are interested in the inherent frequency of low and high mass galaxy pairs in the field, rather than in over dense environments. 
    This will allow us to assess whether there are fundamental differences in the frequency of pairs as a function of mass scale that are independent of environmental factors. 
    As such, we must ensure that our target subhalos are sufficiently isolated.  
    We do this by placing limits on the total mass of the FoF group to which our low mass or high mass samples belong.

    The following selection process is repeated for each snapshot of the simulation over a redshift range of$z=0-\sim4$.  
    We stop our analysis at $z=4.2$ since the population of massive subhalo pairs falls off rapidly at larger redshifts, where the sample size of high mass primaries falls well below 100 subhalos per realization.

    First, at each snapshot, we apply a cut on the total FoF group mass, \MG{}, given by \texttt{Group\_M\_TopHat200}\footnote{The mass \texttt{Group\_M\_TopHat200} is the total mass enclosed by a sphere with mean density $\Delta_c *\rho_c$, where $\Delta_c$ is the overdensity constant from~\citet{Brynorman1998} and $\rho_c$ is the critical density of the universe at the time calculated.} in the TNG100 group catalogs. 
    We define the group mass range for low mass and high mass groups as: 
    \begin{align*}
        \mbox{\textbf{low mass:}}&\,\rm M_{G} = 8\times 10^{10}- 5\times 10^{11}\,\Msun \\ 
        \mbox{\textbf{high mass:}}&\, \rm M_{G}=10^{12}- 6.5\times10^{12}\,\Msun.
    \end{align*}
    The FoF group mass criteria is fixed for all redshifts, which means that some low mass groups at high $z$ may be the progenitors of high mass systems at $z=0$.
    Note that all masses used in this analysis are physical units, meaning that masses from the group catalogs are divided by $h$ to get units of \Msun.

    By requiring that the total FoF group mass does not exceed the above limits, we ensure that there are no subhalos more massive than these limits that will perturb the dynamical state of identified pairs. 
    For example, selecting low mass pairs from the low mass FoF groups ensures that the selected pairs are not satellite systems of high mass subhalos. 
    We have confirmed that over 99\% of subhalos selected from FoF groups that obey the listed mass limits are isolated; meaning, they are not within $1.5\,\Mpc$ of perturbers more massive than the given FoF group.

    % GB removed
  %  Selecting low mass pairs from the low group mass range ensures that we are not selecting satellite systems in the halos of more massive systems, nor low mass pairs in a large group. 
  %  Additionally, $z\sim0$ groups of high mass will host isolated mass analogs of the MW--M31 and MW--LMC systems, while the low mass groups will host isolated mass analogs of an LMC--LMC or LMC--SMC pair.

        % explain what halos we will move forward with. 
    From the set of FoF groups that pass the group mass cut, we create a catalog of all subhalos within each FoF group that pass a current ``minimum mass" threshold.  
    We require that the subhalo mass (\Mhalo\footnote{Note that for the TNG100 hydro run, the subhalo mass is the total sum of all bound dark \textit{and} baryonic matter.}) at the given snapshot, defined by the \texttt{SubhaloMass} field in the group catalogs, is:
    \begin{equation*}
    \mbox{\textbf{minimum subhalo mass:}}\,
    \Mhalo > 1\times10^{9}\Msun.
    \end{equation*}
    This ``minimum mass" threshold ensures that subhalos are resolved into $>100$ particles, and thus should be robustly identifiable using the \subfind\ and \sublink\ algorithms \citep{RG2015}.

    % GB edited
    For each subhalo that passes both criteria, i.e. the subhalo belongs to either a high mass or low mass FoF group and also passes the ``minimum mass" threshold, we use the \sublink\ merger trees to identify the maximum subhalo mass achieved by the subhalo, \Mpeak. 
    We consider only the given snapshot and all previous snapshots in the determination of \Mpeak.

    All subhalos in a given snapshot that pass both the FoF group and ``minimum mass" selection criteria form our full sample of subhalos, which we call the \subcat. 
    The catalog contains subhalos at each snapshot from $z=0-\sim4.2$ (snapshot numbers 20-99) and their associated properties, namely: Subhalo ID, FoF Group Number, current subhalo mass \Mhalo, and peak halo mass \Mpeak. 
    At z=0, this selection process results in 44656 subhalos in low mass groups and 38350 subhalos in high mass groups.

    From here, we will use further selection criteria to narrow down this large sample and to identify pairs of subhalos in each group.
% End choosing halos     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    Primarily, applying an abundance matching prescription to assign stellar masses allows us to account for the observed spread in the SMHM relationship. 
    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, between $\sim 0.3$ for $M_{h}\sim 10^{10}\Msun$ up to $\sim 1$dex for $M_{h}\sim10^{8}\Msun$~\citep{Munshi2021}. 
    While the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5}, using stellar masses as calculated from abundance matching allows us to side step any simulation-dependent stellar mass effects. 
    Finally, utilizing an abundance matching prescription enables direct comparisons of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical way. 
    We make a brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation, in Sec.~\ref{sec:disc-dark}.

    We use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
    The~\citet{Moster2013} relationship is a function of subhalo mass, redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.

    Because the abundance matching prescription is calibrated for centrals of FoF groups, we elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot \citep[see][]{Besla2018}.
    We also use the current redshift of the given snapshot, $z_{snap}$, of each subhalo in the stellar mass calculation. 
    Thus, $\ms{}=f(\Mpeak,z_{snap})$.

>>>>

% Packages
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{hyperref}

@@

% Affiliations
\newcommand{\affuofa}{University of Arizona, 933 N. Cherry Ave, Tucson, AZ 85721, USA}
\newcommand{\affunam}{Instituto de Radioastronom\'ia y Astrof\'isica, Universidad Nacional Aut\'onoma de M\'exico, Apdo. Postal 72-3, 58089 Morelia, Mexico}
\newcommand{\affuoff}{Department of Astronomy, University of Florida, P.O. Box 112055, Gainesville, FL 32611, USA}
\newcommand{\affberk}{Department of Astronomy, University of California, Berkeley, 501 Campbell Hall, Berkeley, CA, 94720, USA}
\newcommand{\affuofu}{Department of Physics and Astronomy, University of Utah, 115 South 1400 East, Salt Lake City, Utah 84112, USA}
\newcommand{\affnyu}{The Center for Cosmology and Particle Physics, New York University, 726 Broadway, New York, NY 10003}
\newcommand{\affnrao}{National Radio Astronomy Observatory, 520 Edgemont Road,
Charlottesville, VA 22903, USA}
\newcommand{\affuva}{Department of Astronomy, University of Virginia, 530 McCormick Road, Charlottesville, VA 22904, USA}
\newcommand{\affempty}{Empty}
\newcommand{\affnottingham}{School of Physics and Astronomy, University of Nottingham, University Park, Nottingham NG7 2RD, UK}
\newcommand{\affkorea}{Korea Astronomy and Space Science Institute, 776 Daedeokdae-ro, Yuseong-gu, Daejeon 34055, Korea}
\newcommand{\afftrent}{Department of Physics and Astronomy, Trent University, 1600 West Bank Drive, Peterborough, ON K9L 0G2, Canada}
\newcommand{\affoccidental}{Occidental College, Physics Department, 1600 Campus Road, Los Angeles, CA 90041, USA}

%% This is the end of the preamble.

@@

\title{
  % Pair fractions of low mass and high mass galaxy pairs in the TNG100 cosmological simulation
  % low mass and high mass galaxy pairs evolve differently as a function of redshift
  A physically motivated framework for measuring\\ the mass and redshift dependence of galaxy pair fractions across cosmic time 
  % A physically motivated framework for measuring galaxy pair fractions across cosmic time
   % for measuring galaxy pair fractions across cosmic time
   % measuring or recovering?
  }
% Differences in the redshift evolution of low mass and high mass galaxy pairs in the TNG100 cosmological simulation

\author[0000-0001-8765-8670]{Katie~Chamberlain}
\thanks{E-mail: katiechambe@arizona.edu}\affiliation{\affuofa}

@@

\author[0000-0002-9820-1219]{Ekta~Patel}
\thanks{Hubble Fellow}\affiliation{\affberk} \affiliation{\affuofu}

\author[0000-0002-9495-0079]{Vicente Rodriguez-Gomez}
\affiliation{\affunam}

\author[0000-0002-5653-0786]{Paul Torrey}
\affiliation{\affuoff}

\author[0000-0003-2939-8668]{Garreth Martin}
\affiliation{\affnottingham}\affiliation{\affkorea}\affiliation{\affuofa}

\author[0000-0001-8348-2671]{Kelsey Johnson}
\affiliation{\affuva}

\author[0000-0002-1871-4154]{Dave Patton}
\affiliation{\afftrent}

\author[0000-0003-0256-5446]{Sarah Pearson}
\thanks{Hubble Fellow}\affiliation{\affnyu}

\author[0000-0003-3474-1125]{George Privon}
\affiliation{\affnrao}\affiliation{\affuoff}\affiliation{\affuva}

\author[0000-0002-2596-8531]{Sabrina Stierwalt}
\affiliation{\affoccidental}

\begin{abstract} 
Low mass galaxy pair fractions are under-studied across cosmic time. 
In the era of JWST, Roman, and Rubin, a self-consistent framework is needed to select both low and high mass galaxy pairs to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts. 
We use the Illustris TNG100 simulation to identify pairs between $z=0-4.2$ that are physically associated, free from contamination owing to projection effects.
We construct a sample of low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) isolated subhalo pairs, using abundance matching to assign stellar masses. 
The low mass pair fraction, i.e. the fraction of galaxies in pairs, increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. 
At $z=0$ the low mass major (1:4 mass ratio) pair fraction is 4$\times$ lower than that of high mass pairs, consistent with findings for cosmological merger rates. 
Our results indicate that pair fractions can faithfully reproduce trends in merger rates if galaxy pairs are selected appropriately. 
Specifically, static pair separation limits applied equivalently to all galaxy pairs do not recover the evolution of low and high mass pair fractions. 
Instead, we advocate for separation limits that vary with the mass and redshift of the system, such as separation limits scaled by the virial radius of the host halo ($r_{\mathrm{sep}}< 1 R_{\rm vir}$).
Finally, we place isolated mass-analogs of Local Group galaxy pairs (i.e., MW--M31, MW--LMC, LMC--SMC) in a cosmological context,

%  changed by rec. of garreth
and show that isolated analogs of LMC--SMC-mass pairs, as well as MW--LMC-mass pairs with low separation ($<50\kpc$), are $2-3\times$ more common at $z\gtrsim2-3$.
%quantifying for the first time the frequency of finding isolated analogs of such pairs as a function of redshift.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{sec:intro}
    Galaxy mergers have been studied in detail as a mechanism for driving galaxy evolution, and have been identified as a trigger of, for example, 
    active galactic nuclei (AGN)~\citep[e.g.][]{Hopkins2008,Treister2010,Ramos2011,Satyapal2014,Comerford2015,Glikman2015,Blecha2018,Ellison2019}, 
    star formation~\citep[e.g.][]{Mihos1996, DiMatteo2008,Ellison2011,Patton2013, Hopkins2013,Martin2017,Patton2020,Hani2020,Martin2021}, 
    and changes in morphology~\citep[e.g.][]{Conselice2003,Lotz2008,Casteels2014,Patton2016,Bignone2017,RG2017,Martin2018,Jackson2019,Snyder2019,Jackson2022,Guzman-Ortega2023}. 
    Constraining the merger rate for galaxies is critical for quantifying the importance of mergers for galaxy evolution and testing predictions for hierarchical assembly in cold dark matter theory \citep[e.g.][]{Stewart2009,Hopkins2010,RG2015}.

    In practice, merger rates cannot be measured straightforwardly from observations and, rather, are calculated by converting the observed frequency of a galaxy merger signature (i.e., asymmetry, concentration, pair fraction, etc.) to a merger rate using an observability timescale~\citep[e.g.][]{Lotz2011}. However, morphological signatures of mergers are often caused by non-merger phenomena.
    For example, low mass galaxies are more commonly morphologically disturbed by fly-bys and non-merger interactions than by mergers~\citep{Martin2021}, 
    and star-forming galaxies at high redshift tend to be clumpy and asymmetric even in isolation~\citep{Wuyts2013}.
    Additionally, detection of these signatures can be strongly dependent on image depth or galaxy stellar mass, and identifying tidal features that rely on human classifications may be unreliable~\citep{Martin2022}.

    Pair fractions, on the other hand, can be calculated independently of morphological information, and thus offer a more robust method of observationally quantifying merger rates across cosmic time. 
    Pair fractions of high mass ($M_*\gtrsim10^{10}\Msun$) galaxies have been well studied across cosmic time both observationally~\citep[e.g.][]{Patton2002,Lin2004,Lin2008,Lotz2011,Ferreras2014, Man2016,Duncan2019}, and theoretically~\citep[e.g.][]{RG2015,Snyder2017,Snyder2023}, with theoretical studies typically done in projection for comparison to observational campaigns\footnote{The studies cited here have limits on the projected separation of their sample, such that the projected separations range between $5\,\kpc$ and $\sim140\,\kpc$.}.  
    Low mass galaxy pairs ($10^8<M_*<5\times10^9\Msun$) have been studied at low redshift~\citep[e.g.][]{Stierwalt2015,Pearson2016,Besla2018,Paudel2018,Luber2022},
    but are less well understood across cosmic time owing to the difficulty in observing faint systems outside of the Local Volume. 
    However, JWST~\citep{Gardner2006}, as well as the next generation of deep and wide-field surveys from Rubin Observatory\footnote{ \href{https://rubinobservatory.org/}{https://rubinobservatory.org}}~\citep{RUBIN2019} and Roman Space Telescope\footnote{\href{https://roman.gsfc.nasa.gov/}{https://roman.gsfc.nasa.gov}}~\citep{Spergel2015}, will significantly revolutionize our ability to identify such systems at high redshift $(z\gtrsim10)$~\citep{Behroozi2020} and in abundance at lower redshift ($z\lesssim6$)~\citep{Robertson2019a,Robertson2019b-LSST}.

    There are reasons to believe that low mass and high mass pairs evolve differently as a function of time.
    For example, semi-empirical and cosmological studies find that galaxy merger rates vary both with redshift and the mass of the most massive galaxy of the pair~\citep[see e.g.][]{Guo2008,Stewart2009,Hopkins2010,RG2015,Martin2021}.
    % Such differences are likely to give rise to differences in the pair fractions of low and high mass pairs.
    It is thus reasonable to assume that the pair fractions of these two mass scales reflect these evolutionary differences as well.

@@

    Typically, observational studies of pair fractions apply projected separation cuts that are constant over time and do not vary with the mass of the target system. 
    To fairly test for differences in the evolutionary behavior of pair fractions, especially in observational studies, it is necessary to determine whether this is an appropriate technique for accurately recovering true pair fraction behavior.
    In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and make recommendations for a time and mass evolving separation cut to permit equitable pair fraction comparisons between different mass regimes.

    In particular, we take the approach of consistently selecting physically associated pairs of low mass ($10^8<M_*<5\times10^9\Msun$) and high mass $(5\times10^9<M_*<10^{11}\,\Msun)$ galaxies. 
    Specifically, we identify major ($1-1/4$) and minor $(1/10-1/4)$ stellar mass ratio pairs from $z=0-4.2$ in the IllustrisTNG cosmological simulation, TNG100. 
    We require that pairs are part of the same Friends of Friends (FoF) group and that no other more massive perturbers are nearby, which allows us to ensure that the recovered pair fractions are inherent to the population of selected pairs rather than a function of environment.

@@

    This paper is structured as follows. 
    In Section~\ref{sec:methods}, we outline our methodology for selecting physically associated high mass and low mass pairs from the TNG simulation. 
    In Section~\ref{sec:pairprops}, we provide an overview of the properties of the selected sample, including the number of primaries, pairs, and their stellar mass ratios as a function of time. 
    We present the time-evolving pair fraction of high mass and low mass pairs in Section~\ref{sec:results}, and show how they change for different separation criteria. 
    In Section~\ref{sec:discussion}, we discuss the implications of the differences between low and high mass pair fractions for observational campaigns and give context to our results by drawing comparisons to Local Group pairs. 
    Finally, we summarize our results and conclusions in Section~\ref{sec:summary}.

@@

\section{Methodology}\label{sec:methods}
We aim to quantify and characterize the frequency, or pair fraction, of low mass ($\rm\ms{}=10^{8}-5\times 10^{9}\Msun$) and high mass ($\rm\ms{}=5\times10^{9}-10^{11}\Msun$) galaxy pairs in cosmological simulations as a function of cosmic time. 
To this end, we utilize the \tng\ suite of simulations to select subhalo pairs as a function of redshift, according to the selection criteria outlined in the remainder of this section.

@@

%%%%%%%%%%%%%%%%%%%%%%%
% Sim details section %
    \subsection{Simulation details} \label{sec:methods-sims}
        % Brief description of TNG hydro and which run we use.
    The IllustrisTNG project~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body and full physics cosmological simulations that adopt the \textit{Planck2015} \lcdm\  cosmology~\citep{Planck2015}.

    In this study, we utilize data from TNG100-1, the main high resolution, full physics simulation of a $(110.7\,\Mpc)^3$ volume (hereafter TNG100)\footnote{We will also use data from TNG100-1-Dark, the main high resolution dark-matter-only run (hereafter TNG100-Dark), as presented in Sec.~\ref{sec:disc-dark}.} 
    This simulation follows the evolution of baryons and $1820^3$ dark matter particles from $z=127$ to $z=0$.  
    The volume of this simulation is sufficiently large, and the resolution is sufficiently high, to conduct a simultaneous analysis of the statistics of both low mass and high mass galaxy pairs, as shown by studies of pair statistics in similarly sized volumes~\citep{Sales2013,Patel2017a-Orbits,Patel2017b-Masses,Besla2018}.

      % subfind, sublink, and groups and subhalos
    We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm~\citep{Springel2001,Dolag2009}. 
    This catalog was created using the Friends-of-Friends (FoF) algorithm~\citep{Davis1985}, which links nearby dark matter particles to define large halos of associated particles, from which subhalos are identified as over-dense and gravitationally bound dark matter structures.
    In addition, we utilize the merger trees provided by the \texttt{SUBLINK} algorithm~\citep{RG2015}, which tracks subhalos between snapshots, enabling us to trace the mass evolution of our selected subhalos.

% End sim details     %
%%%%%%%%%%%%%%%%%%%%%%%

@@

    In this section, we outline the steps to create the \subcat, which we will utilize to assign stellar masses to each of the dark matter subhalos.

    We are interested in the intrinsic frequency of low and high mass galaxy pairs in the field, rather than in over dense environments. 
    This allows us to assess whether there are fundamental differences in the frequency of pairs as a function of mass scale that are independent of environmental factors\footnote{Note that our pair fraction calculations are thus specifically for isolated systems, and the global pair fraction (including both isolated and non-isolated pairs) will be different.}.
    As such, we must ensure that our target subhalos are sufficiently isolated.  
    We do this by placing limits on the virial mass of the FoF group to which our low mass or high mass samples belong.

    The following selection process is repeated for each snapshot of the simulation over a redshift range of $z=0-4.2$.  
    We stop our analysis at $z=4.2$ since the population of massive subhalo pairs falls off rapidly at larger redshifts, where the sample size of high mass primaries falls well below 100 subhalos per snapshot.

    First, at each snapshot, we apply a cut on the FoF group virial mass, $M_{\rm vir}$, given by \texttt{Group\_M\_TopHat200}\footnote{The mass \texttt{Group\_M\_TopHat200} is the mass enclosed by a sphere with mean density $\Delta_c *\rho_c$, where $\Delta_c$ is the overdensity constant from~\citet{Brynorman1998} and $\rho_c$ is the critical density of the universe at the time calculated. The corresponding virial radius in TNG100 is given by \texttt{Group\_R\_TopHat200}.} in the TNG100 group catalogs. 
    We define the group mass range for low mass and high mass groups as: 
    \begin{align*}
        \mbox{\textbf{low mass:}}&\,\rm M_{G} = 8\times 10^{10}- 5\times 10^{11}\,\Msun \\ 
        \mbox{\textbf{high mass:}}&\, \rm M_{G}=10^{12}- 6.5\times10^{12}\,\Msun.
    \end{align*}
    The FoF group mass criteria is fixed for all redshifts, which means that some low mass groups at high $z$ may be the progenitors of high mass systems at $z=0$.
    % Note that all masses used in this analysis are physical units, meaning that masses from the group catalogs are divided by $h$ to get units of \Msun.

    By requiring that the FoF group virial mass does not exceed the above limits, we ensure that there are no subhalos more massive than these limits that will perturb the dynamical state of identified pairs. 
    For example, selecting low mass pairs from the low mass FoF groups ensures that the selected pairs are not satellite systems of high mass subhalos. 
    We have confirmed that over 99\% of subhalos selected from FoF groups that obey the listed mass limits are isolated; meaning, they are not within $1.5\,\Mpc$ of perturbers more massive than the mass of the pair.

    From the set of FoF groups that pass the group mass cut, we create a catalog of all subhalos within each FoF group that pass a current ``minimum mass" threshold.  
    At the given snapshot, we require a minimum subhalo mass \Mhalo\ to be:
    \begin{equation*}
    \mbox{\textbf{minimum subhalo mass:}}\,
    \Mhalo > 1\times10^{9}\Msun.
    \end{equation*}
    \Mhalo\ is given by the \texttt{SubhaloMass} field in the group catalogs, and is the total combined mass of all bound dark \textit{and} baryonic matter.
    This ``minimum mass" threshold ensures that subhalos are resolved into $>100$ dark matter particles, and thus should be robustly identifiable using the \subfind\ and \sublink\ algorithms~\citep{RG2015}.

    For each subhalo that passes both criteria, i.e. the subhalo belongs to either a high mass or low mass FoF group and also passes the ``minimum mass" threshold, we use the \sublink\ merger trees to identify the maximum subhalo mass achieved by the subhalo, \Mpeak. 
    We consider only the given snapshot and all previous snapshots in the determination of \Mpeak.

    All subhalos in a given snapshot that pass both the FoF group and ``minimum mass" selection criteria form our full sample of subhalos, which we call the \subcat. 
    The catalog contains subhalos at each snapshot from $z=0-\sim4.2$ (snapshot numbers 20-99) and their associated properties, namely: Subhalo ID, FoF Group Number, current subhalo mass \Mhalo, and peak subhalo mass \Mpeak. 
    At z=0, this selection process results in 44656 subhalos in low mass groups and 38350 subhalos in high mass groups.

    From here, we will use additional selection criteria to identify pairs of subhalos in each group.
% End choosing halos     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    Primarily, applying an abundance matching prescription to assign stellar masses allows us to account for the observed spread in the SMHM relationship. 
    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, between $\sim 0.3$ for $M_{h}\sim 10^{10}\Msun$ up to $\sim 1$dex for $M_{h}\sim10^{8}\Msun$~\citep{Munshi2021}. 
    While the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5,Nelson2019}, using stellar masses as calculated from abundance matching allows us to avoid any simulation-dependent stellar mass effects. 
    Finally, utilizing an abundance matching prescription enables direct comparisons of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical way. 
    We make a brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation, in Sec.~\ref{sec:disc-dark}.

    We use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
    The~\citet{Moster2013} relationship is a function of subhalo mass, redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with a larger scatter at lower halo masses.

    Because the abundance matching prescription is calibrated for centrals of FoF groups, we elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot \citep[see][]{Besla2018}.
    We also use the current redshift of the given snapshot, $z_{\mathrm{snap}}$, of each subhalo in the stellar mass calculation. 
    Thus, $\ms{}=f(\Mpeak,z_{\mathrm{snap}})$.
